Flowchart of Current Algorithm

### 2009-01-22 docs/flowchart/flowchart.tex
some cosmetic changes to the equations just because I'm overly particular

\item We have added the flag, {\tt full\_rhoh0\_evolution}, which defaults to 
{\tt TRUE} (note that we do not have a {\bf Correct Base} or 
{\bf Diffuse Base} for enthalpy).  When {\tt FALSE}, we do not call {\bf React Base},
but instead set $(\rho h)_0 = (\overline{\rho h})^n$ before {\bf Advect Base}.

@@

$\etarho$ & $\etarho \equiv (\overline{ \rho' \Ubt \cdot \er})$ & g~cm$^{-2}$~s$^{-1}$ \\

@@

\item For any quantity, $\phi,$ we define $\overline{\phi} = ${\bf Avg}$(\phi),$ 
the average over $\Omega_H,$ as
\begin{equation}
\overline{\phi}(r) 
= \frac{1}{\mathrm{A}(\Omega_H)}\int_{\Omega_H} \phi(r,{\bf x}) \; dA \enskip .
\end{equation}
here $\Omega_H$ is a layer at constant radius $r$.  In plane-parallel, this is 
as straightforward as averaging cell values at a particular height.  For spherical 
problems, see the description in Section \ref{Sec:Avg}.

@@

\item {\bf React Base}$[(\rho h)_0^{\inp},(\overline{\rho\Hnuc})^{\inp},(\overline{\rho\Hext})^{\inp}] \rightarrow [(\rho h)_0^{\outp}]$\\
is the process by which we update the base state enthalpy through $\dt/2$ in time using
\begin{equation}
\frac{\partial(\rho h)_0}{\partial t} = (\overline{\rho\Hnuc})^{\inp} + (\overline{\rho\Hext})^{\inp}\enskip ,
\end{equation}
discretized as
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} + \frac{\dt}{2}(\overline{\rho\Hnuc})_{j}^{\inp} + \frac{\dt}{2}(\overline{\rho\Hext})_{j}^{\inp} \enskip .
\end{equation}

@@

\item Define
\begin{equation}
\overline{S}^{\nph,\star} = {\mathrm{\bf Avg}} \left(S^{\nph,\star}\right) \enskip .
\end{equation}

@@

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g 
\enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh}$ and the volume discrepancy correction with $f=0.3$,
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S}^{\nph,\star} 
- \frac{1}{\gammabar^{n} p_0^{n}}
\left\{ \psi^{\nmh} + 
f \left[\frac{p_0^n - \overline{p(\rho,h,X_k)}^n}{\Delta t^n} \right]\right\}
\enskip .
\end{equation}

@@

The procedure to construct $\uadvone$ is described in detail in Appendix B of paper III.
We note that  $\uadvone$ satisfies the discrete versions of 
\begin{equation}
\int_{\Omega_H} \Ubt \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}
(paper III; eq.~[21])
and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt )  = \beta_0 \left(S - \Sbar \right )\enskip ,
\label{eq:tildeconstraint}
\end{equation}
(paper III; eq.~[39]).  The discretization with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star} - \overline{S}^{\nph,\star}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)}^n}{\Delta t^n}\right]\right\} \enskip .
\end{equation}

@@

~~~ {\bf React Base}$[(\rho h)_0^n,(\overline{\rho \Hnuc})^{(1)},(\overline{\rho\Hext})^n] \rightarrow [(\rho h)_0^{(1)}]$ \\
{\bf else}

~~~ $(\rho h)_0^{(1)} = (\overline{\rho h})^{(1)}$\\
{\bf end if}
\item Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

\item Define
\begin{eqnarray}
 \gammabar^{n+1,\star}    &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{n+1,\star}, p_0^{n+1,\star}, 
                                                      X_k^{n+1,\star}) \right] \enskip , \\
 {\beta   }_0^{n+1,\star}    &=& \beta   \left(\rho_0^{n+1,\star}, p_0^{n+1,\star}, \gammabar^{n+1,\star}\right) \enskip .
\end{eqnarray}

@@

\item Define
\begin{equation}
\overline{S}^{\nph} = {\mathrm{\bf Avg}} (S^{\nph}) \enskip.
\end{equation}

@@

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}) with the 
volume discrepancy correction,
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = 
\overline{S}^{\nph,\star} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left\{ \psi^{\nph,\star} + f \left[\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)}^{\nph,\star}}{\Delta t^n}\right]\right\}
\enskip ,
\end{equation}
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}
\end{equation}
\begin{equation}
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}
\end{equation}
\begin{equation}
\overline{p(\rho,h,X_k)}^{\nph,\star} = 
\frac{\overline{p(\rho,h,X_k)}^n + \overline{p(\rho,h,X_k)}^{n+1,\star}}{2}
\end{equation}

@@

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=&
\beta_0^{\nph,\star}\left\{\left(S^{\nph} - \overline{S}^{\nph}\right)
 + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}\cdot \right. \nonumber \\
&& \left.\left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)}^{\nph,\star}}{\Delta t^n}\right]\right\} \enskip ,
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\item {\bf React Base}$[(\rho h)_0^{(2)},(\overline{\rho \Hnuc})^{(2)},(\overline{\rho\Hext})^{(2)}] \rightarrow [(\rho h)_0^{n+1}]$

\item Define
\begin{eqnarray}
 \gammabar^{n+1}    &=& {\rm{\bf Avg}}\left[\Gamma_1(\rho^{n+1}, p_0^{n+1}, {X_k}^{n+1}) \right] \enskip , \\ 
 {\beta   }_0^{n+1}    &=& \beta   \left(\rho_0^{n+1}, p_0^{n+1},   \gammabar^{n+1}\right) \enskip .
\end{eqnarray}

@@

\item Define
\begin{equation}
\overline{S}^{n+1} = {\mathrm{\bf Avg}} (S^{n+1}) \enskip.
\end{equation}

@@

Finally, we impose the divergence constraint from equation (\ref{eq:tildeconstraint}) 
including the volume discrepancy correction,
\begin{equation}
\nablab \cdotb \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S}^{n+1} \right)
+ \frac{f}{\gammabar^{n+1} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)}^{n+1}}{\Delta t^n}\right]\right\}
\enskip,
\end{equation}
by defining ${\bf V} = \Ubt^{n+1,\star} + ( \dt / \rho^\nph ) \; \mathbf{G} \pi^\nmh$ 
and solving
\begin{equation}
 L_\beta^\rho \phi =
   D \left ( \beta_0^{\nph} {\bf V} \right) - \beta_0^{\nph}\left\{ \left(S^{n+1}-\overline{S}^{n+1} \right)
- \frac{f}{\gammabar^{n+1} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)}^{n+1}}{\Delta t^n}\right]\right\} \enskip, \label{Linear System for Multigrid}
\end{equation}
for nodal values of $\phi$, where
$\beta_0^\nph = ( \beta_0^n + \beta_0^{n+1} )/2$ and
$L_\beta^\rho$ is the standard bilinear
finite element approximation to $\nablab \cdotb ({\beta_0^\nph}/{\rho^\nph}) \nablab.$
In this step, $D$ is a discrete second-order operator that approximates the 
divergence at nodes from cell-centered data and satisfies
$\mathbf{G} = -D^T.$ 
(See (cite almgrenBellSzymczak:1996) for a detailed discussion of this
approximate projection; see (cite almgren:bell:crutchfield) for a discussion
of this particular form of the projection operand.)  
We solve the linear system of equation (\ref{Linear System for Multigrid})
using multigrid V-cycles with Gauss-Seidel relaxation.

@@

  \item Compute $\overline{S}^{0,\nu} = {\mathrm{\bf Avg}} (S^{0,\nu}).$

  \item Compute $w_0^{\nu+1}$ as in step 1c using $\overline{S}^{0,\nu}$ and $\psi^{\nmh} = 0$.

  \item Project $\Ub^{0,\nu}$ using $\beta_0^{\initp}$ and 
        $(S^{0,\nu} - \overline{S}^{0,\nu})$ as the source term.  
        This yields $\Ub^{0,\nu+1}.$

@@

  \begin{enumerate}
  \item Perform steps 1--11 as described above, using 
    $S^{\myhalf,\star} = (S^0 + S^{1,\nu})/2$ in step 1 as described.
    The only other difference in the time advancement is that in step 11
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi =
      D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ \left(S^{1}-\overline{S}^{1}\right) - \left(S^{0}-\overline{S}^{0}\right) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard,  and new values for $\etarho^{\myhalf}$ (step 8), $\psi^{\myhalf}$ (step 8), 
      $S^{1,\nu+1}$ (step 10), and $\pi^{\myhalf}$ (step 11), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}

>>>>

\item We have added the flag, {\tt full\_rhoh0\_evolution}, which defaults to 
{\tt TRUE} (note that we do not have a {\bf Correct Base} or 
{\bf Diffuse Base} for enthalpy).  When {\tt FALSE}, we do not call {\bf React Base},
but instead set $(\rho h)_0 = \overline{(\rho h)^n}$ before {\bf Advect Base}.

@@

$\etarho$ & $\etarho \equiv \overline{(\rho' \Ubt \cdot \er)}$ & g~cm$^{-2}$~s$^{-1}$ \\

@@

\item For any quantity, $\phi,$ we define $\overline{\phi} = ${\bf Avg}$(\phi),$ 
the average over $\Omega_H,$ as
\begin{equation}
\overline{\phi(r)}
= \frac{1}{\mathrm{A}(\Omega_H)}\int_{\Omega_H} \phi(r,{\bf x}) \; dA \enskip .
\end{equation}
here $\Omega_H$ is a layer at constant radius $r$.  In plane-parallel, this is 
as straightforward as averaging cell values at a particular height.  For spherical 
problems, see the description in Section \ref{Sec:Avg}.

@@

\item {\bf React Base}$[(\rho h)_0^{\inp},\overline{(\rho\Hnuc)^{\inp}},\overline{(\rho\Hext)^{\inp}}] \rightarrow [(\rho h)_0^{\outp}]$\\
is the process by which we update the base state enthalpy through $\dt/2$ in time using
\begin{equation}
\frac{\partial(\rho h)_0}{\partial t} = \overline{(\rho\Hnuc)^{\inp}} + \overline{(\rho\Hext)^{\inp}}\enskip ,
\end{equation}
discretized as
\begin{equation}
(\rho h)_{0,j}^{\outp} = (\rho h)_{0,j}^{\inp} + \frac{\dt}{2}\overline{(\rho\Hnuc)_{j}^{\inp}} + \frac{\dt}{2}\overline{(\rho\Hext)_{j}^{\inp}} \enskip .
\end{equation}

@@

\item Compute
\begin{equation}
\overline{S^{\nph,\star}} = {\mathrm{\bf Avg}} \left(S^{\nph,\star}\right) \enskip .
\end{equation}

@@

\item[plane-parallel:] We integrate
\begin{equation}
\frac{\partial w_0}{\partial r} =  \Sbar - \frac{1}{\gammabar p_0} \etarho g 
\enskip \label{eq:divw0} ,
\end{equation}
using the lagged $\psi^{\nmh}$ and the volume discrepancy correction with $f=0.3$,
\begin{equation}
\frac{\partial w_0^{\nph,\star}}{\partial r} =  \overline{S^{\nph,\star}}
- \frac{1}{\gammabar^{n} p_0^{n}}
\left\{ \psi^{\nmh} + 
f \left[\frac{p_0^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n} \right]\right\}
\enskip .
\end{equation}

@@

The procedure to construct $\uadvone$ is described in detail in Appendix B of paper III.
We note that  $\uadvone$ satisfies the discrete versions of 
\begin{equation}
\int_{\Omega_H} \Ubt \cdotb \er \; dA = 0 \label{eq:udoterzero} \enskip ,
\end{equation}
(paper III; eq.~[21])
and
\begin{equation}
\nablab \cdotb (\beta_0 \Ubt )  = \beta_0 \left(S - \Sbar \right )\enskip ,
\label{eq:tildeconstraint}
\end{equation}
(paper III; eq.~[39]).  The discretization with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^n \uadvone\right) = 
\beta_0^n \left\{ \left(S^{\nph,\star} - \overline{S^{\nph,\star}}\right)
+ \frac{f}{\gammabar^n p_0^n}
\left[\frac{p(\rho,h,X_k)^n - \overline{p(\rho,h,X_k)^n}}{\Delta t^n}\right]\right\} \enskip .
\end{equation}

@@

~~~ {\bf React Base}$[(\rho h)_0^n,\overline{(\rho \Hnuc)^{(1)}},\overline{(\rho\Hext)^n}] \rightarrow [(\rho h)_0^{(1)}]$ \\
{\bf else}

~~~ $(\rho h)_0^{(1)} = \overline{(\rho h)^{(1)}}$\\
{\bf end if}
\item Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

\item Define
\begin{eqnarray}
 \gammabar^{n+1,\star}    &=& {\rm{\bf Avg}} \left[ \Gamma_1\left(\rho^{n+1,\star}, p_0^{n+1,\star}, 
                                                      X_k^{n+1,\star}\right) \right] \enskip , \\
 {\beta   }_0^{n+1,\star}    &=& \beta   \left(\rho_0^{n+1,\star}, p_0^{n+1,\star}, \gammabar^{n+1,\star}\right) \enskip .
\end{eqnarray}

@@

\item Compute
\begin{equation}
\overline{S^{\nph}} = {\mathrm{\bf Avg}} (S^{\nph}) \enskip.
\end{equation}

@@

\item[plane-parallel:] We integrate equation (\ref{eq:divw0}) with the 
volume discrepancy correction,
\begin{equation}
\frac{\partial w_0^{\nph}}{\partial r} = 
\overline{S^{\nph,\star}} - \frac{1}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left\{ \psi^{\nph,\star} + f \left[\frac{p_0^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\}
\enskip ,
\end{equation}
\begin{equation}
\gammabar^{\nph,\star} = \frac{\gammabar^{n} + \gammabar^{n+1,\star}}{2}
\end{equation}
\begin{equation}
p_0^{\nph,\star} = \frac{p_0^{n} + p_0^{n+1,\star}}{2}
\end{equation}
\begin{equation}
\overline{p(\rho,h,X_k)^{\nph,\star}} = 
\frac{\overline{p(\rho,h,X_k)^n} + \overline{p(\rho,h,X_k)^{n+1,\star}}}{2}
\end{equation}

@@

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=&
\beta_0^{\nph,\star}\left\{\left(S^{\nph} - \overline{S^{\nph}}\right)
 + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}\cdot \right. \nonumber \\
&& \left.\left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)^{\nph,\star}}}{\Delta t^n}\right]\right\} \enskip ,
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\item {\bf React Base}$[(\rho h)_0^{(2)},\overline{(\rho \Hnuc)^{(2)}},\overline{(\rho\Hext)^{(2)}}] \rightarrow [(\rho h)_0^{n+1}]$

\item Define
\begin{eqnarray}
 \gammabar^{n+1}    &=& {\rm{\bf Avg}}\left[\Gamma_1\left(\rho^{n+1}, p_0^{n+1}, {X_k}^{n+1}\right) \right] \enskip , \\ 
 {\beta   }_0^{n+1}    &=& \beta   \left(\rho_0^{n+1}, p_0^{n+1},   \gammabar^{n+1}\right) \enskip .
\end{eqnarray}

@@

\item Compute
\begin{equation}
\overline{S^{n+1}} = {\mathrm{\bf Avg}} (S^{n+1}) \enskip.
\end{equation}

@@

Finally, we impose the divergence constraint from equation (\ref{eq:tildeconstraint}) 
including the volume discrepancy correction,
\begin{equation}
\nablab \cdotb \left(\beta_0^{\nph} \Ubt^{n+1} \right)  = \beta_0^{\nph}\left\{  \left(S^{n+1} - \overline{S^{n+1}} \right)
+ \frac{f}{\gammabar^{n+1} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\}
\enskip,
\end{equation}
by defining ${\bf V} = \Ubt^{n+1,\star} + ( \dt / \rho^\nph ) \; \mathbf{G} \pi^\nmh$ 
and solving
\begin{equation}
 L_\beta^\rho \phi =
   D \left ( \beta_0^{\nph} {\bf V} \right) - \beta_0^{\nph}\left\{ \left(S^{n+1}-\overline{S^{n+1}} \right)
- \frac{f}{\gammabar^{n+1} p_0^{n+1}}
\left[\frac{p(\rho,h,X_k)^{n+1} - \overline{p(\rho,h,X_k)^{n+1}}}{\Delta t^n}\right]\right\} \enskip, \label{Linear System for Multigrid}
\end{equation}
for nodal values of $\phi$, where
$\beta_0^\nph = ( \beta_0^n + \beta_0^{n+1} )/2$ and
$L_\beta^\rho$ is the standard bilinear
finite element approximation to $\nablab \cdotb ({\beta_0^\nph}/{\rho^\nph}) \nablab.$
In this step, $D$ is a discrete second-order operator that approximates the 
divergence at nodes from cell-centered data and satisfies
$\mathbf{G} = -D^T.$ 
(See (cite almgrenBellSzymczak:1996) for a detailed discussion of this
approximate projection; see (cite almgren:bell:crutchfield) for a discussion
of this particular form of the projection operand.)  
We solve the linear system of equation (\ref{Linear System for Multigrid})
using multigrid V-cycles with Gauss-Seidel relaxation.

@@

  \item Compute $\overline{S^{0,\nu}} = {\mathrm{\bf Avg}} (S^{0,\nu}).$

  \item Compute $w_0^{\nu+1}$ as in step 1c using $\overline{S^{0,\nu}}$ and $\psi^{\nmh} = 0$.

  \item Project $\Ub^{0,\nu}$ using $\beta_0^{\initp}$ and 
        $(S^{0,\nu} - \overline{S^{0,\nu}})$ as the source term.  
        This yields $\Ub^{0,\nu+1}.$

@@

  \begin{enumerate}
  \item Perform steps 1--11 as described above, using 
    $S^{\myhalf,\star} = (S^0 + S^{1,\nu})/2$ in step 1 as described.
    The only other difference in the time advancement is that in step 11
    we define ${\bf V} = (\Ubt^{1,\star} - \Ubt^0)$ and solve
    \begin{equation}  L_\beta^\rho \phi =
      D \left ( \beta_0^{\myhalf} {\bf V} \right) - \beta_0^{\myhalf} \left[ \left(S^{1}-\overline{S^{1}}\right) - \left(S^{0}-\overline{S^{0}}\right) \right] \enskip . 
    \end{equation}
    (The motivation for this form of the projection in the initial pressure iterations
    is discussed in (cite almgren:bell:crutchfield).)
      We discard the new velocity resulting from this, but keep the new  
      value for $\pi^{\myhalf} = \pi^{-\myhalf} + (1 / \dt) \; \phi.$  
      These steps also yield new scalar data at time $\dt,$ which
      we discard,  and new values for $\etarho^{\myhalf}$ (step 8), $\psi^{\myhalf}$ (step 8), 
      $S^{1,\nu+1}$ (step 10), and $\pi^{\myhalf}$ (step 11), which we keep.
    \item Set $\pi^{-\myhalf} = \pi^{\myhalf}$, $\etarho^{-\myhalf} = \etarho^{\myhalf}$,
      and $\psi^{-\myhalf} = \psi^{\myhalf}$. 
    \end{enumerate}
